Numerical trajectory patterns of floating macroalgae

### 2020-11-16 thesis_chapter_3.Rmd
added eddy script. script tidy for simulation data

# Read in data and data wrangling

p_RK4 <- tidync("OceanParcels/trajectory_data/RK4_PFloat.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Min_Kfloat_H100_W00 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Min_Kfloat_H095_W05 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H095_W05.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Min_Kfloat_H090_W10 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H090_W10.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Min_Kfloat_H085_W15 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H085_W15.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Mean_Kfloat_H100_W00 <- tidync("OceanParcels/trajectory_data/Mean_KFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Mean_KFloat_H095_W05 <- tidync("OceanParcels/trajectory_data/Mean_KFloat_H095_W05.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Mean_KFloat_H090_W10 <- tidync("OceanParcels/trajectory_data/Mean_KFloat_H090_W10.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Mean_KFloat_H085_W15 <- tidync("OceanParcels/trajectory_data/Mean_KFloat_H085_W15.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Max_Kfloat_H100_W00 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Max_Kfloat_H095_W05 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H095_W05.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Max_Kfloat_H090_W10 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H090_W10.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

Max_Kfloat_H085_W15 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H085_W15.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))

@@

```{r summary wrangle, message= FALSE, warning = FALSE, echo = FALSE}

p_RK4_mean <- p_RK4 %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Min_Kfloat_H100_W00_mean <- Min_Kfloat_H100_W00 %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Min_Kfloat_H095_W05_mean <- Min_Kfloat_H095_W05 %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Min_Kfloat_H090_W10_mean <- Min_Kfloat_H090_W10 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Min_Kfloat_H085_W15_mean <- Min_Kfloat_H085_W15 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Mean_Kfloat_H100_W00_mean <- Mean_Kfloat_H100_W00 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Mean_KFloat_H095_W05_mean <- Mean_KFloat_H095_W05 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Mean_KFloat_H090_W10_mean <- Mean_KFloat_H090_W10 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Mean_KFloat_H085_W15_mean <- Mean_KFloat_H085_W15 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_Kfloat_H100_W00_mean <- Max_Kfloat_H100_W00 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_Kfloat_H095_W05_mean <- Max_Kfloat_H095_W05 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_Kfloat_H090_W10_mean <- Max_Kfloat_H090_W10 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_Kfloat_H085_W15_mean <- Max_Kfloat_H085_W15 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

>>>>

# load and data wrangle for eddy simulation

p_eddy <- tidync("OceanParcels/trajectory_data/PassiveEddy.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
p_eddy_mean <- p_eddy %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

p_eddy$type <- "Passive Eddy" # add extra column 'type' to dataframe

Min_KFloat_Eddy <- tidync("OceanParcels/trajectory_data/Min_KFloat_Eddy.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
Min_K_Eddy_mean <- Min_KFloat_Eddy %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Min_KFloat_Eddy$type <- "Min_KFloat_Eddy" # add extra column 'type' to dataframe

Mean_KFloat_Eddy <- tidync("OceanParcels/trajectory_data/Mean_KFloat_Eddy.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
Mean_KFloat_Eddy_mean <- Mean_KFloat_Eddy %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Mean_KFloat_Eddy$type <- "Mean_KFloat_Eddy" # add extra column 'type' to dataframe

Max_KFloat_Eddy <- tidync("OceanParcels/trajectory_data/Max_KFloat_Eddy.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
Max_KFloat_Eddy_mean <- Max_KFloat_Eddy %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_KFloat_Eddy$type <- "Max_KFloat_Eddy" # add extra column 'type' to dataframe

# Read in simulation data and data wrangling

p_RK4 <- tidync("OceanParcels/trajectory_data/RK4_PFloat.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
p_RK4_mean <- p_RK4 %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Min_Kfloat_H100_W00 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Min_Kfloat_H100_W00_mean <- Min_Kfloat_H100_W00 %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Min_Kfloat_H095_W05 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H095_W05.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Min_Kfloat_H095_W05_mean <- Min_Kfloat_H095_W05 %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Min_Kfloat_H090_W10 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H090_W10.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Min_Kfloat_H090_W10_mean <- Min_Kfloat_H090_W10 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Min_Kfloat_H085_W15 <- tidync("OceanParcels/trajectory_data/Min_KFloat_H085_W15.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Min_Kfloat_H085_W15_mean <- Min_Kfloat_H085_W15 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Mean_Kfloat_H100_W00 <- tidync("OceanParcels/trajectory_data/Mean_KFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Mean_Kfloat_H100_W00_mean <- Mean_Kfloat_H100_W00 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Mean_KFloat_H095_W05 <- tidync("OceanParcels/trajectory_data/Mean_KFloat_H095_W05.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Mean_KFloat_H095_W05_mean <- Mean_KFloat_H095_W05 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Mean_KFloat_H090_W10 <- tidync("OceanParcels/trajectory_data/Mean_KFloat_H090_W10.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Mean_KFloat_H090_W10_mean <- Mean_KFloat_H090_W10 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Mean_KFloat_H085_W15 <- tidync("OceanParcels/trajectory_data/Mean_KFloat_H085_W15.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Mean_KFloat_H085_W15_mean <- Mean_KFloat_H085_W15 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Max_Kfloat_H100_W00 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Max_Kfloat_H100_W00_mean <- Max_Kfloat_H100_W00 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Max_Kfloat_H095_W05 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H095_W05.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Max_Kfloat_H095_W05_mean <- Max_Kfloat_H095_W05 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Max_Kfloat_H090_W10 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H090_W10.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Max_Kfloat_H090_W10_mean <- Max_Kfloat_H090_W10 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

Max_Kfloat_H085_W15 <- tidync("OceanParcels/trajectory_data/Max_KFloat_H085_W15.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Max_Kfloat_H085_W15_mean <- Max_Kfloat_H085_W15 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

@@

```{r eddy plots, message=FALSE, warning=FALSE, include=FALSE}

passive_eddy <- ggplot() + 
  geom_point(data = p_eddy, aes(x = lon, y = lat)) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Passive") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

min_eddy <- ggplot() + 
  geom_point(data = Min_K_Eddy, aes(x = lon, y = lat)) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Minimum Ac") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

mean_eddy <- ggplot() + 
  geom_point(data = Mean_KFloat_Eddy, aes(x = lon, y = lat)) +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Mean Ac") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

max_eddy <- ggplot() + 
  geom_point(data = Max_KFloat_Eddy, aes(x = lon, y = lat)) +
  xlab("Longtitude") + 
  ylab("Latitude") +
  ggtitle("Maximum Ac") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggarrange(passive_eddy, min_eddy, mean_eddy, max_eddy)
```
